Incremental λ-Calculus in Cache-Transfer Style

### 2017-07-10 popl18/static-differentiation.tex
cts-case-studies: abstract over benchmark file location
Rename conflicting labels from POPL draft

\subsection{Static differentiation in \source}
Previous work~\citep{CaiEtAl2014ILC} defines differentiation for simply-typed
$\lambda$-calculus terms.
Figure~\ref{fig:differentiation} shows differentiation for $\source$'s syntax.

\input{differentiation}
Differentiating a base term~$\sterm$ produces a change
term~$\iderive{\sterm}$, its \emph{derivative}.
%
Differentiating final result variable~$\tx$ produces its change variable~$\tdx$.
Differentiation copies each binding of an intermediate result $\ty$ to the
output and adds a new bindings for its change $\tdy$.
%
If $\ty$ is bound to tuple~$\stuple{\many\tx}$, then $\tdy$ will
be bound to the change tuple $\stuple{\many\tdx}$.
If $\ty$ is bound to function application $\sapp\tf{\tx}$, then $\tdy$ will be
bound to the application of function change $\tdf$ to input $\tx$ and its change
$\tdx$.

>>>>

\subsection{Static differentiation in \source}
Previous work~\citep{CaiEtAl2014ILC} defines differentiation for simply-typed
$\lambda$-calculus terms.
Figure~\ref{fig:popl-differentiation} shows differentiation for $\source$'s syntax.

\input{\poplPath{differentiation}}
Differentiating a base term~$\sterm$ produces a change
term~$\iderive{\sterm}$, its \emph{derivative}.
%
Differentiating final result variable~$\tx$ produces its change variable~$\tdx$.
Differentiation copies each binding of an intermediate result $\ty$ to the
output and adds a new bindings for its change $\tdy$.
%
If $\ty$ is bound to tuple~$\stuple{\many\tx}$, then $\tdy$ will
be bound to the change tuple $\stuple{\many\tdx}$.
If $\ty$ is bound to function application $\sapp\tf{\tx}$, then $\tdy$ will be
bound to the application of function change $\tdf$ to input $\tx$ and its change
$\tdx$.
